It took months to learn the basics. In skateboarding, you don't have a coach or trainer, it's just you against yourself. In skateboarding, when you mess up you get hurt.

You get hurt pretty often.

But it's worth it~--- every scar, every scare, every sore muscle. Skateboarding is a constant battle: trying and failing, trying and failing. Up the quarter pipe and pivot incorrectly: disaster. If you're lucky you bail and run it off. The other times your front foot sticks to the board and takes off without you. If you're lucky you slide. If you're me, your PCL gets torn. But you can't let that stop you. Lay out for a bit and stretch, walk it off, then skate it off. This is the punishment we all signed up for. It comes with the territory.

The quarter pipe is mean. Meaner than an inanimate object has any right to be. It is unrelenting. Ruthless. Yet it draws me in, makes me want to attack it, to hurt myself, to succeed. There is nothing like this addiction.

So I push off. That smooth, familiar feeling of a skateboard glassing across a box. I try to time the transitions; I've been through enough pain today, no sense in adding more. It's down the ramp and over the pyramid. Approach the quarter pipe, pump, hit the apex, pivot, balance, and ride down.

Pure, unadulterated ecstasy as I ride back to the box. I have finally ridden my first quarter pipe. Heart quivering, knees aching, and this goofy smile spreads across my stupid face. But the day is long from over: I must practice and practice again. I can't let this enemy hurt me anymore.
