\textbf{Exhale.} Here goes. Kick twice, reposition, tuck, untuck, pivot, oh frick! Bail!

Run off a bit, grab my board\dots\ alright, let's do it again.

Push off~--- kick once, balance\dots\ balance!~--- kick again. Position your feet, moron. Ramp coming up, but you're going a little too fast so don't bend your knees. Let the transition slow you down. \textbf{click click} Pivot, straighten out. \textbf{click click}. Kick. Kick again. Not too bad that time. Fag.

Alright, straighten out. Let's try to do this straight on.

Breathe, man! Here we go.

Bend, unbend, pivot.

Dammit.

\textbf{Exhale.} Reposition the board. No, that's too much. \textbf{Shake my head.} Fix it. No, fix it. \textbf{Roll my eyes.} Push off. You know the drill: kick, balance, kick, balance, kick again, balance, transition, pivot, transition, kick. Kick, ride. Bend, unbend, pivot, nope, bail.

Maybe that was a little too casual.

Ride back, doo-tee-doo, pivot, fail. Really? How do you biff that? Alright, let's do this. Correctly this time. Push off, kick twice, ride. Get ready.

Crouch, stand up, pivot. Holy hell! Watch it.

Dammit, you almost had it that time.

Alright, ride back. Don't do the ramp this time~--- let's just concentrate on the bowl.

This is it. This is the one. You're gonna get it this time. You suck, but you're gonna get it this time.

Push off, kick. Kick again. Straighten out. Feet in the right positions. Heh, positions. Crouch, stay crouched through the transition, pivot. Ride off.

\begin{center}Holy crap.\end{center}
