Yesterday sucked.

Let me explain. I went to the skatepark on my lunch break to work on the quarter pipe. For the past week I haven't been able to land anything. I'm close, but I can't land it.

\emph{Today's the day. Been working on this for six days now and this is it. This is the one.}

How na\"\i{}ve. How prideful to think that after only a week I could do this. It took months~--- literally months~--- to learn how to ride, to push, to balance. And finally, finally has skateboarding become a little more natural, a little more second nature. When I get to the skatepark, I don't have to ride for fifteen minutes just to get used to the feeling of a board under my feet. What a wonderful return on investment to learn and grow! But that was an investment of four months, of sweat, of blood, just to learn how to ride.

\emph{Alright, it took two weeks to pivot on a ramp. The quarter pipe is not too different; it's a smooth transition and a pivot at the apex. Sure, the apex is steeper than the incline of a ramp, but skateboarding is natural now; it's what I do. I can do this.}

Learning how to ride a quarter pipe is not going to be conquered in one day, but it should not have been as painful as it was. I had stood around for too long chatting with the new kid in town; finished that conversation, knees a little stiff, ankles not fully cooperating, and rode off down the box. I glassed over the pyramid and approached the quarter.

\emph{Holy mother of hell this hurts. I don't think I can stand up. I better not end up in the ER.}
