On the quarter pipe, pivoting, pivoting, not pivoting enough. When I bailed, I didn't clear the board and my front foot landed back on the board. My back leg twisted in as the board took off and I almost did the splits.

\emph{Really hoping that kid doesn't come over here and try to help me. I freaking got this. I don't need his hel\dots\ dang it, he's coming over.}

A few weeks before this I was in Alaska tromping along the side of a river. I stepped into what I figured would be four inch deep water, max. It turned out to be closer to four feet. My left foot plummeted, my right foot slammed into my chest. My right knee can naturally get about a foot and a half away from my chest~--- there should not be any touching, let alone slamming.

\emph{I don't know if I can walk. How am I going to get home? I have to freaking ride my bike home and my hip isn't working. Let's try standing.}

Seven years ago while hiking in the High Sierras, I destroyed my hip. After my mission it had gotten bad enough that I had to go to physical therapy. Now I'm lying on the ground incapable of standing; just having a real bang up time with this.

\emph{``Nah, man~--- I'm fine,'' I say, falling over. ``On second thought, can you give me a hand?''}

After dusting myself off, I packed my gear and took off. Riding home, the cool breeze blowing through my hair, I limp along. I think I'll be just fine. This is part of the territory, after all; the pain will subside and I will get that quarter pipe one way or another.
